Security Audit of Safeplug

### 2014-01-14 results.tex
split results in half

\section{Results}
\label{sec:results}
\subsection{User Experience}
TODO: Annie
    -Terms of Service
    -Setup to home router
    -Using the internet
    -Experience
    -Cookie experience (Fourthparty)

\subsection{Teardown}
TODO: Annie
    -Parts in the box
    -Possible attacks via USB/SD Card

\subsection{Traffic Analysis}
TODO: Anna
    -What's the udpate?
    -Phone home frequency
    -Does it do anything else?
    -How does the ad-blocking work?

\subsection{Gaining Access through SSH}
TODO: Anna
    -How we got access
    -What's the software
    -What/where are the settings
    -RPC server
        -Attacks from anyone on local network
        -Attack from a website?

>>>>

\section{Results}
\label{sec:results}
\subsection{User Experience}
\label{sec:ux}
TODO: Annie
    -Terms of Service
    -Setup to home router
    -Using the internet
    -Experience
    -Cookie experience (Fourthparty)

\subsection{Teardown}
\label{sec:tear}
TODO: Annie
    -Parts in the box
    -Possible attacks via USB/SD Card

\begin{figure}[htb]
\begin{center}
\includegraphics[width=\linewidth]{safeplug_top}
\caption{This is a figure.}
\end{center}
\end{figure}

\begin{figure}[htb]
\begin{center}
\includegraphics[width=\linewidth]{safeplug_bottom}
\caption{This is a figure.}
\end{center}
\end{figure}
